---
title: "quickerstats"
author: "Aaron Anderson"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{quickerstats}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Introduction
The USDA's National Agricultural Statistics Service collects a wide variety of
data on US agriculture. They maintain a web tool (Quick Stats, see 
https://quickstats.nass.usda.gov/) as well as an API 
(see https://quickstats.nass.usda.gov/api) for accessing the data. Both of the
existing tools for pulling data are cumbersome due to their design and the
variety of data available. The goal of quickerstats is to provide an tool for
pulling data that is easier to use.

An important parameter of the Quick Stats is 'short_desc' (called Data Item
in the web tool), which is a concatenation six other parameters (commodity_desc, 
class_desc, prodn_practice_desc, util_practice_desc, statisticcat_desc, 
and unit_desc). A typical workflow would be to 

## Installation

## Functions


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(quickerstats)
```
